### 2011-06-05 thesis/novelty-intro.tex
Explained independent approach for the unconditional factor.

\section{Novelty Detection as a Threshold}

% Explain threshold approach to novelty detection
Due to the desire of robustness, a novelty detection system is often given the option
to classify non-novel samples as novel. This is implemented as a threshold that describes a trade
between error and rejection: the more the system tries to reduce rejection, the more
prone to produce errors it becomes.

@@

Nonetheless such an approach suffers from
the \emph{curse of dimensionality} as the number of sensed features and feature
types increases.

A relaxed solution can be obtained by assuming in that the sensed features are
independent conditional 
Although the sensed variables are considered independent given the room category
$r$, when $r$ is not able to model  hidden
variable $r$. The approach should then be to 
In order to correctly approach the unconditional probability the unlabelled
data should be used 
Without the assumption of the room category being known it is no longer easy
to model the distribution between all sensed variables.
Under the assumption

Note that although sensed variables are independent, they are only so when $r$
is given. Requiring a factor to be connect between all variables to model their
dependence.

@@

\begin{description}
\item[exact]
$P(x|\overline{novel})/P(x)$
Since the distribution is synthetic there is access to $P(x)$ and $P(x|concept)$
and a perfect threshold function could also be created to test how far the
presented thresholds are from optimal.

\item[uniform]
$P_G(x)/P_U(x)$ assuming a uniform unconditional distribution

\item[independent]
$P_G(x)/P_I(x)$ assuming an independent unconditional distribution.
\end{description}

>>>>

\section{Novelty Detection as a Threshold}
% Explain threshold approach to novelty detection
Due to the desire of robustness, a novelty detection system is often given the option
to classify non-novel samples as novel. This is implemented as a threshold that describes a trade
between error and rejection: the more the system tries to reduce rejection, the more
prone to produce errors it becomes.

@@

Nonetheless such an approach suffers from
the \emph{curse of dimensionality}: as the number of sensed features and feature
types increases exponential ammounts of data are needed to describe it.
Having interest in avoiding the issues associated with an high-connected factor
an assumption on independent features can be done and then the unconditional
probability can be modelled with a fully disconnected variables, but with
factors that account for existent bias on each single feature (as visible on
graph in \autoref{fig:simple-independent-graph}).

Note than in the case there is only one sensed feature, the distribution
probability modelled by an assumption of independent features correctly models
unconditional probability. And it deviates from it as more features are sensed.
Though the individual factors associated with each variable try to unwrapped any
possible existent bias on each dimension and therefore it is expected to be a
better estimate than assuming a uniform distribution.

@@

\begin{description}
\item[exact] 
- since the distribution is synthetic there is access to $P(x)$ and $P(x|concept)$
and the ordering function $P(x|\overline{novel})/P(x)$ could be created
to test how far the other presented thresholds are from optimal.

\item[uniform]
- by assuming a uniform unconditional distribution the ordering function is
  given by $P_G(x)/P_U(x)$.

\item[independent]
- using the unlabelled data the unconditional distribution can be approximated.
  In this case, it was approximated with an independent distribution of the
  sensed features. The independent threshold was implemented with $P_G(x)/P_I(x)$.
\end{description}
